King Dengklek once planted N trees, conveniently numbered 0 through N-1, along the main highway in the Kingdom of Ducks. As time passed, the trees grew beautifully. Now, the height of the i-th tree is heights[i] units. 

King Dengklek now thinks that the highway would be even more beautiful if the tree heights were in strictly ascending order. More specifically, in the desired configuration the height of tree i must be strictly smaller than the height of tree i+1, for all possible i. To accomplish this, King Dengklek will cast his magic spell. If he casts magic spell of level X, he can increase or decrease the height of each tree by at most X units. He cannot decrease the height of a tree into below 1 unit. Also, the new height of each tree in units must again be an integer. 

Of course, a magic spell of a high level consumes a lot of energy. Find and print the smallest possible non-negative integer X such that King Dengklek can achieve his goal by casting his magic spell of level X.

\subsection* {Input}

The input will consist in several test cases; each test case will consist of a line with the given sequence of heights. You can assume the following conditions will always be true:
heights will contain between 2 and 50 elements, inclusive.
Each elements of heights will be between 1 and 1,000,000,000, inclusive.

\subsection* {Output}

For each test case, print one line with the answer, follow the format on the output example.

\outputnotice

\vspace{12pt}
\begin{minipage}[c]{1\textwidth}%
	\begin{center}
		\begin{tabular}{|l|l|} \hline 
		\begin{minipage}[t]{0.6\textwidth}%
		\bf{Input sample} \\
		\begin{verbatim}
9 5 11
5 8
1 1 1 1 1
548 47 58 250 2012

\end{verbatim}
    \end{minipage}%


    \begin{minipage}[t]{0.3\textwidth}%
      \textbf{Output sample} \\      
\begin{verbatim}
3
0
4
251

\end{verbatim}
\end{minipage}\\
    \hline
\end{tabular}\end{center}\end{minipage}%
