Bob's father bought him a toy map of islands and seas. The map is a two-dimensional grid where each cell is either 'x' or '.'. A sea is defined as a maximal connected group of '.' cells, where two '.' cells are connected if they are vertically or horizontally adjacent. An island is defined as a maximal connected group of 'x' cells, where two 'x' cells are connected if they are vertically, horizontally, or diagonally adjacent. An island has a level of 0 if it contains no other islands. An island has a level of K+1 if it contains one or more islands and the highest level of a contained island is K. An island A contains island B if A and B are different and, if you start sailing from any point of island B, you won't be able to sail out of island A (you can sail only horizontally and vertically, but not diagonally).

For example, the given map below has 5 islands with level 0 (islands 0 - 4 on the right picture) and one island with level 1 (island 5). Please note that starting at island 3, you can not sail outside island 5 (you can not sail diagonally), but its possible get out of island 1 when starting at island 4.

\begin{verbatim}
xxx.x...xxxxx        000.0...11111
xxxx....x...x        0000....1...1
........x.x.x        ........1.4.1
..xxxxx.x...x        ..55555.1...1
..x...x.xxx.x        ..5...5.111.1
..x.x.x...x..        ..5.3.5...1..
..x...x...xxx        ..5...5...111
...xxxxxx....        ...555555....
x............        2............
\end{verbatim}

Given seaMap, find and print several integers (may be one), where the k-th element is the number of islands of level k. The output to the problem must contain exactly (m + 1) elements, where m is the highest level of an island in the map.

\subsection* {Input}

The input will consist in several test cases; each test case will consist of a line with R and C,between 1 and 50, the numbers of rows and cols of the given seaMap, the next R lines will contain the given seaMap. You can assume the following conditions will always be true:
seaMap will contain between 1 and 50 elements, inclusive.
Each element of seaMap will contain between 1 and 50 characters, inclusive.
Each element of seaMap will contain the same number of characters.
Each element of seaMap will contain only '.' and lowercase 'x' characters.

\subsection* {Output}

For each test case, print one line with the answer, follow the format on the output example.

\outputnotice

\vspace{12pt}
\begin{minipage}[c]{1\textwidth}%
	\begin{center}
		\begin{tabular}{|l|l|} \hline 
		\begin{minipage}[t]{0.6\textwidth}%
		\bf{Input sample} \\
		\begin{verbatim}
1 1
x
5 5
xxxxx
x...x
x.x.x
x...x
xxxxx
10 5
xxxxx
x...x
x.x.x
x...x
xxxxx
xxxxx
x...x
x.x.x
x...x
xxxxx
2 2
..
..
6 12
............
.......xxxx.
..xxx.x...x.
..x..x..x.x.
..x.x.x...x.
..xx...xxx..

\end{verbatim}
    \end{minipage}%


    \begin{minipage}[t]{0.3\textwidth}%
      \textbf{Output sample} \\      
\begin{verbatim}
{1}
{1, 1}
{2, 1}
{}

\end{verbatim}
\end{minipage}\\
    \hline
\end{tabular}\end{center}\end{minipage}%
