We have a String, let’s call it originalWord. Each character of originalWord is either 'a' or 'b'. Timmy claims that he can convert it to finalWord using exactly k moves. In each move, he can either change a single 'a' to a 'b', or change a single 'b' to an 'a'.

You are given the Strings originalWord and finalWord, and the integer value k. Determine whether Timmy may be telling the truth. If there is a possible sequence of exactly k moves that will turn originalWord into finalWord, print "POSSIBLE" (quotes for clarity). Otherwise, print "IMPOSSIBLE".

\subsection* {Input}

The input will consist in several test cases; each test case will consist of a line with originalWord, finalWord and k, each token will be separated by a single space and there will not be leading or trailing spaces. You can assume the following conditions will always be true:
Timmy may change the same letter multiple times. Each time counts as a different move.
originalWord will contain between 1 and 50 characters, inclusive.
finalWord and originalWord will contain the same number of characters.
Each character in originalWord and finalWord will be 'a' or 'b'.
k will be between 1 and 100, inclusive.

\subsection* {Output}

For each test case, print one line with the answer, follow the format on the output example.

\outputnotice

\vspace{12pt}
\begin{minipage}[c]{1\textwidth}%
	\begin{center}
		\begin{tabular}{|l|l|} \hline 
		\begin{minipage}[t]{0.6\textwidth}%
		\bf{Input sample} \\
		\begin{verbatim}
aababba bbbbbbb 2
aabb aabb 1
aaaaabaa bbbbbabb 8
aaa bab 4
aababbabaa abbbbaabab 9

\end{verbatim}
    \end{minipage}%


    \begin{minipage}[t]{0.3\textwidth}%
      \textbf{Output sample} \\      
\begin{verbatim}
IMPOSSIBLE
IMPOSSIBLE
POSSIBLE
POSSIBLE
IMPOSSIBLE


\end{verbatim}
\end{minipage}\\
    \hline
\end{tabular}\end{center}\end{minipage}%
